manuscript

### 2023-12-05 scripts/manuscript.qmd
Created table, put plots with results, added figure #s to plots.

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(janitor)
library(ggplot2)
library(papaja)
```

@@

```{r}
#for ben to do later: create summarize data frames to create into a table
```

# Data Visualizations

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Invasive Behaviors Score",
       title = "Boxplot of Teacher Invasive Behaviors Score by Gender")

ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender")

ggplot(communication, aes(gender, ppis_total, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Privacy Invasion Scale Total",
       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender")

ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender")

model <- lm(ppis_total ~ ss_score, comm)
modelresults <- apa_print(model)
slope <- coef(model)[2] %>% round(2)

ggplot(comm, aes(ss_score, ppis_total)) +
  geom_point() +
  geom_smooth(method = "lm", color="darkgreen") +
  labs(title = "Student's Trustworthiness and Teacher Privacy Invasions", 
       x = "Own Precieved Trustworthiness",
       y = "Teacher Privacy Invasions") +
   geom_text(x = 30, y = 4,
     label = sprintf("Slope: %.2f", coef(lm(ppis_total ~ ss_score, data = comm))[2])) +
  theme_minimal()

mean_age <- mean(comm$age) %>% round(2)
sd_age <- sd(comm$age) %>% round(2)

@@

@@

### Modified Parental Privacy Invasions Scale

@@

### Modified Suspicion Scale

@@

@@

Privacy invasions and self-rated trustworthiness were not found to be correlated. Self-rated trustworthiness was not a significant predictor of privacy invasions (`r modelresults$full_result$ss_score`).

Gender differences existed for teacher invasive behaviors. Non-binary individuals perceived their teachers behaviors as being less invasive than females and males perceptions. Gender differences existed for teacher privacy invasion. Males perceived their teachers invading their privacy less than female and non-binary individuals. There were gender differences in the amount of suspicion towards teachers. Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion.

There were no gender differences in student defensive behaviors.

>>>>

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(janitor)
library(ggplot2)
library(papaja)
library(gt)
library(gtExtras)
```

@@

```{r}
ppis_ss_table <- communication %>%
select(ppis_1_score:ppis_total) %>%
  pivot_longer(
  cols = everything(),
  names_to = "measure",
  values_to = "score") %>%
  group_by(measure) %>%
  summarise(Mean = mean(score, na.rm = TRUE),
            SD = sd(score, na.rm = TRUE)) %>%
  pivot_longer(
    cols = -measure,
    names_to = "desc",
    values_to = "value"
    ) %>%
  pivot_wider(names_from = measure,
              values_from = value)
```

@@

```{r}
#| echo: false
#| warning: fale
#| message: false
mean_age <- mean(comm$age) %>% round(2)
sd_age <- sd(comm$age) %>% round(2)
```

@@

### Modified Parental Privacy Invasions Scale: Teacher Privacy Invasions Scale (TPIS)

@@

### Modified Suspicion Scale (SS)

@@

```{r}
model <- lm(ppis_total ~ ss_score, comm)
modelresults <- apa_print(model)
slope <- coef(model)[2] %>% round(2)
```

@@

## Descriptive Statistics

The means and standard deviations of the TPIS scores and the SS Scores can be shown in Table 1 below.

```{r}
#| output: asis
desc_table <- 
  gt(ppis_ss_table) %>%
  cols_label(desc = "Statistic", ppis_1_score = "Teacher Privacy Invasions", ppis_2_score = "Student Trustworthiness", ppis_total = "TPIS Total", ss_score = "Suspicion Scale") %>%
  tab_caption(caption = "Descriptive Statistics of TPIS and SS Scores ") %>%
  tab_footnote(footnote = "Table 1.")

desc_table
```

## Teacher Privacy Invasions and Suspicion Scale

Privacy invasions and self-rated trustworthiness were not found to be correlated. Self-rated trustworthiness was not a significant predictor of privacy invasions (`r modelresults$full_result$ss_score`). A scatterplot of the relationship can be seen in Figure 1, shown below.

ggplot(comm, aes(ss_score, ppis_total)) +
  geom_point() +
  geom_smooth(method = "lm", color="darkgreen") +
  labs(title = "Student's Trustworthiness and Teacher Privacy Invasions", 
       x = "Own Precieved Trustworthiness",
       y = "Teacher Privacy Invasions",
       tag = "Figure 1.") +
   geom_text(x = 30, y = 4,
     label = sprintf("Slope: %.2f", coef(lm(ppis_total ~ ss_score, data = comm))[2])) +
  theme_minimal()
```

## Gender Differences

Gender differences existed for teacher invasive behaviors. Non-binary individuals perceived their teachers behaviors as being less invasive than females and males perceptions. Gender differences existed for teacher privacy invasion. Males perceived their teachers invading their privacy less than female and non-binary individuals. A boxplot of Teacher Invasive Behaviors scores, split by gender, can be found in Figure #. There were no gender differences in student defensive behaviors. A boxplot of this relationship can be found below in Figure #. There were also no differences in the total Teacher Privacy Invasion scale scores between gender groups, shown in the boxplot in Figure #.

There were gender differences in the amount of suspicion towards teachers. Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion. A boxplot of mean Suspicion Scale scores, split by gender, can be found in Figure # below.

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Invasive Behaviors Score",
       title = "Boxplot of Teacher Invasive Behaviors Score by Gender", 
       tag = "Figure 2.")
```

ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender",
       tag = "Figure 3.")

ggplot(communication, aes(gender, ppis_total, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Privacy Invasion Scale Total",
       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender",
       tag = "Figure 4.")

ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender",
       tag = "Figure 5.")
